Changing Flights In The Air\\ (Abortable Chain Agreement)

### 2015-05-09 paper/abstract2.tex
Work on the abstract

    The key novelty of our framework is its practical applicability, having state
    of the art optimization and reconfiguration techniques built-in: tolerating k fault with k+1
    replicas using an external reconfiguration master, executing commutative commands 
    without synchronization, optimizing the execution of read-only commands,
    minimizing the size of crucial data structures.

>>>>

    The key novelty of our framework is its practical applicability, having state
    of the art optimization and reconfiguration techniques built-in:
    primary-backup replication, tolerating k fault with k+1
    replicas using an external reconfiguration master, executing commutative commands 
    without synchronization, optimizing the execution of read-only commands,
    minimizing the size of crucial data structures.

    \begin{itemize}
      \item Checkpointing
      \item Primary-backup replication with expeditive reads, k-fault tolerance with
        k+1 replicas.
      \item Latency of two messages when contention happens only on commutative
        commands.
    \end{itemize}
